Boundary terms in the action for Causal Sets

### 2014-10-13 paper_v7.tex
edits in section 1-2

In furthering causal set theory it is crucial that we understand the kinematics of the theory. The action of a given causal set (also causet) is a crucial piece of the kinematics that would be extremely useful to know and understand. Proposals for the action of a causal set are available \cite{Benincasa_Dowker:The_Scalar_Curvature_of_a_Causal_Set} and these hold analytically in some cases and numerically in many more.\mb{rephrase} One can show that the action of the causal set then agrees with the Einstein-Hilbert action of the spacetime in some continuum limit. How this limiting procedure is carried out will be described in more detail below.

It is well known that the Einstein-Hilbert action, $S_{EH}$, is not the full story in the continuum. In the presence of spacetime boundaries the gravitational action must include a boundary term $S_{GHY}$, the Gibbons-Hawking-York action, in order to yield a well-defined variational principle~\cite{Gibbons_Hawking_Boundary}. The contributions of this term play an essential role in particular in the quantum theory. For instance, in the calculation of the black hole entropy via the Euclidean path-integral, it is the boundary terms that produce the answer $A/4l_p^2$ necessary for the unification of black hole mechanics with thermodynamics. To give another example, in Regge calculus boundary terms are necessary in order that the quantum mechanical amplitudes satisfy the correct composition law and that they have the correct classical limit~\cite{hartlesorkin}.\mb{is this true?}

@@

In order to say we have a causal set analogue for a continuous expression we need a well defined procedure for relating the discrete theory to the continuum. This procedure, or tool, is called a \textit{Poisson sprinkling}, or just a \textit{sprinkling}. It is a Poisson process which provides a way to generate a causet from a $d$-dimensional Lorentzian manifold $ (M,g)$ by selecting certain points in $M$ to be the elements of $\mathcal{C}$, with an order relation given by the causal order of the manifold. The number of points chosen in a region of spacetime volume, $V$, is a Poisson random variable. This means that the expected number of points in some region will be $\rho V$, where $\rho$ is the density of the sprinkling. The density is related to the discreteness scale, $l$, by $\rho=l^{-d}$ in $d$ spacetime dimensions. It is called a sprinkling as one can envisage the point selection process as a `sprinkling' of points into the manifold. If a causet, $\mathcal{C}$, can be generated with relatively high probability by a sprinkling into the manifold, $ (M,g)$, then we say that the manifold is a good approximation for the causal set, and that the causet can be \emph{faithfully embedded} in $M$.

@@

Consider a sufficiently well-behaved $d$-dimensional spacetime $(M,g)$ of finite volume, which admits a \emph{spacelike partitioning} surface, $\Sigma$, defined as a spacelike closed compact surface in $M$, where the causal past and future sets, $M^\pm=J^\pm (\Sigma)$, of the surface then satisfy $M^+\cap M^-=\Sigma$. With this condition it follows that no points in $M^+\setminus\Sigma$ precede any points in $M^-\setminus\Sigma$. If there does exist a $p\in M^+\setminus\Sigma$ and a $q\in M^-\setminus\Sigma$ such that $p\preceq q$, then as $q\in J^-(\Sigma)$ we find that $p\in J^-(\Sigma)$, and hence it is in the set $M^-=J^-(\Sigma)$ by definition. The intersection, $M^+\cap M^-=\Sigma$, is now only true if $p\in\Sigma$ which it does not, and hence there cannot exist such a $p$.  We also have that $\partial M^\pm = \Sigma$. The Gibbons-Hawking-York boundary term for $M^\pm$ is in natural units given by
\be\label{eq:GHYBT_in_continuum}
{S}^{(d)}_{GHY}\left[M^\pm\right]= \mp \frac{1}{l_p^{d-2}}\int_{\Sigma} K d\Sigma
\ee
where $l_p$ is the rationalised Planck length for a general dimension, $l_p=(8\pi G)^{\frac{1}{d-2}}$ (where $G$ is the gravitational constant for a general dimension) and $K$ is the trace of the extrinsic curvature $K_{\mu\nu}=h_{\mu}^\rho h_\nu^\sigma \nabla_\rho n_\sigma$ of $\Sigma$ defined with future-pointing timelike unit normal covector $n_{\mu}=\partial_\mu S/\sqrt{g^{\mu\nu}\partial_\mu S\partial_\nu S}$. (We work with a mostly plus convention for the metric, in which this translates into a past-pointing normal vector $n^{\mu}$). Now observe that the integral in~\eqref{eq:GHYBT_in_continuum} can be thought of as the ``volume gradient'' across the surface $\Sigma$:
\be\label{eq:normal_deriv_boundary}
\int K d\Sigma = \frac{\partial}{\partial n}\int d\Sigma,
\ee
where the right hand side is the derivative of the area $\int d\Sigma$ as each point of $\Sigma$ is moved an equal distance along the unit normal vector, $n^{\mu}$ (corresponding to the rate of change of the surface volume \emph{backwards} in time, as $n^{\mu}$ is past-pointing).

Spacetime volume in the causal set is obtained simply by counting the number of elements, and hence the volume gradient intuitively corresponds to the difference in the number of ``immediate neighbours'' to the future and to the past of a hypersurface. In order to make this notion precise, we need to define the causal set analogue of a hypersurface, as well as an appropriate notion of ``closeness'' to it.

Given a causet that can be faithfully embedded in a manifold $M$ with a spacelike partitioning surface $\Sigma$, we obtain a natural partition of the causet into two parts $\mathcal{C}^+$ and $\mathcal{C}^-$, corresponding to the sets of elements that lie in $M^+=J^+(\Sigma)$ and $M^-=J^-(\Sigma)$. By virtue of $\Sigma$ being spacelike partitioning, the set $\mathcal C^-$ contains its own past, that is, any element in $\mathcal C$ that precedes at least one element in $\mathcal{C}^-$ is also in $\mathcal{C}^-$. Such a set is known as a \emph{past stem}. Similarly, $\mathcal C^+$ is a \emph{future stem} given an analogous definition. We propose more generally that for any causet $\mathcal C$, a \emph{spacelike partition} is a non-trivial partition that splits $\mathcal{C}$ into two parts, $\mathcal{C}^-$ and $\mathcal{C}^+=\mathcal{C}\setminus\mathcal{C}^-$ \IGNORE{($\mathcal{C}=\mathcal{C}^-\cup\mathcal{C}^+$)}, such that $\mathcal{C}^-$ is a past stem (or, equivalently, that $\mathcal{C}^+$ is a future stem and $\mathcal{C}^- = \mathcal{C}\setminus\mathcal{C}^+$). A sprinkling into a manifold with a surface such as $\Sigma$ will of course produce a causal set with spacelike partition, but we shall refer to a partition of a causal set satisfying the above definition as spacelike even when the causet is not obtained via a sprinkling into some manifold.

Determining rules for a partition to correspond to a timelike hypersurface in the continuum is extremely difficult and no satisfactory answer has been found yet. The situation for a null hypersurface is as follows. For any finite density sprinkling into a manifold (that admits a spacelike partitioning surface) with a null hypersurface, $\Sigma$, that null hypersurface will partition the causal set in such a way that agrees with our definition of a spacelike partition.\footnote{This fact means we should really refer to such a partition as ``non-timelike", but as we are dealing with spacelike hypersurfaces for most of this paper we shall continue to call such a partition spacelike}~The reason for this is that a causal set cannot distinguish between a null and spacelike hypersurface. To see why this is imagine a finite density sprinkling into a patch of $2$-dimensional Minkowski spacetime. Figure~\ref{fig:low_density_sprinkling_with_null_and_spacelike} shows how, given a null surface that partitions the causet into two parts, we can tilt the surface slightly so that it is now spacelike, while still preserving the partition. Figure~\ref{fig:high_density_sprinkling_with_null_and_spacelike} shows that even as we increase the density of the sprinkling we can tilt the surface by a smaller amount such that the partition remains unchanged. Hence, for any finite density sprinkling one can always find some slight deviation from a partitioning null hypersurface to one that is spacelike, while still preserving the partition. As the partition does not change we have no way of knowing whether the hypersurface is null or spacelike.

@@

In the continuum the GHY term is usually calculated for the future or past bounding surfaces of a manifold, not for a partitioning surface. We wish to calculate the GHY term for future or past boundaries of causets, but there are a couple issues we must deal with. First, if we can faithfully embed a causet $\mathcal{C}$ into $M$ then the boundary surface of $M$ will induce a trivial partition of $\mathcal{C}$ (every element of $\mathcal{C}$ will lie in the bulk of $M$), thus the previous notion of the boundary term as a rate of change of spacetime atoms across a partition does not work. Second, what does it mean to say a bounding surface of a causet if it is not faithfully embeddable in some manifold? Previously if the causet was not faithfully embeddable we could still define the causal set analogue of the surface as a partition of the causet, but now we have that either $\mathcal{C}^+$ or $\mathcal{C}^-$ will be the empty set. The first issue is not a problem, and we will see that a causal set GHY term can be found for a future (past) boundary of $M$ (the manifold that the causet has been faithfully embedded in) via some other expression in terms of the causet. This expression applies to any causet, and so must apply whether or not the causet is faithfully embeddable, but this runs us into the second issue above. What do we mean by a boundary of a causet? If one is given a causet with maximal and/or minimal elements, certain quantities can be calculated for that causet, like the GHY term we will propose in the next section. We will not provide any physical meaning to a \emph{future} or \emph{past boundary} of a causet, and shall merely state that they are abstract objects for which certain causal set quantities can be calculated. The reason we say that these quantities are being evaluated for the future (past) boundary of the causet is that given a causet that is faithfully embeddable in some manifold with future (past) boundary, the values of the quantities in question will agree with those of certain geometrical quantities for the continuum boundary, in some continuum limit of the causal set. We will henceforth mention future/past boundaries of causets only in the context of some quantity being evaluated for them.

@@

For a given causet $\mathcal C$, let us define the function $\F{k}\left[\mathcal{C}\,\right]$, which counts the number of elements in $\mathcal C$ that have exactly $k$ elements in their future, and the function $\P{k}\left[\mathcal{C}\,\right]$, which counts the number of elements which have exactly $k$ elements in their past. An ``$F_0$ element'' is then a \emph{maximal} element and a ``$P_0$ element'' is a \emph{minimal} element.

Given a causet, $\mathcal{C}$, with a spacelike partition so that $\mathcal C = \mathcal C^+ \cup\, \mathcal C^-$, we propose the following family of functions as the generalised causal set boundary action:
\be\label{general_boundary_sum}
S^{ (d)}_{GHY}\left[\mathcal{C}^-,\mathcal{C}^+;\vec{p}, \vec{q}\,\right]= \left (l/l_p\right)^{d-2} c_{d}
\left ( \sum_m p_m \F{m}\left[\mathcal{C}^- \right]
+  \sum_n q_n \P{n}\left[\mathcal{C}^+ \right]\right)
\ee
where the constant $c_{d}$ only depends on the spacetime dimension and is given by
\be\label{Cn}
c_{d}=\frac{d (d+1)}{ (d+2)}\left(\frac{V_{d-1}}{d}\right)^{\frac{2}{d}},
\ee
$V_d=\pi^{\frac{d}{2}}/\Gamma\left (\frac{d}{2}+1\right)$ denotes the volume of the unit $d$-ball and $\Gamma (t)$ is the gamma function. We have used $\vec{p}$ and $\vec{q}$ to stand for infinite dimensional vectors $ (p_0,...,p_m,..)$ and $ (q_0,...,q_n,..)$ respectively, where all the $p_m,\: q_n \in \mathbb{R}$. These vectors contain a finite number of non-zero entries, corresponding to the coefficients of the different $\F{m}$ and $\P{n}$ terms. We use the summation $\sum_m$ ($\sum_n$) to denote a sum that runs from $0$ to $m_{max}$ ($n_{max}$), where $m_{max}$ ($n_{max}$) is some integer, the value of which depends on the causet $\mathcal{C}^-$ ($\mathcal{C}^+$), for which all $\F{m}\left[\mathcal{C}^- \right]=0$ ($\P{n}\left[\mathcal{C}^+ \right]=0$) for any $m>m_{max}$ ($n>n_{max}$). Finite values for $m_{max}$ and $n_{max}$ will always exist for any finite causet. The vectors must be chosen such that they satisfy the following conditions.
\begin{align}\label{coefficient_relation1}
& \sum_m p_m \frac{\Gamma\left (\frac{1}{d}+m \right)}{m!}  + \sum_n q_n\frac{\Gamma\left (\frac{1}{d}+n \right)}{n!}=0
\\
& \label{coefficient_relation2}\sum_m p_m \frac{\Gamma\left (\frac{2}{d}+m \right)}{m!}  - \sum_n q_n\frac{\Gamma\left (\frac{2}{d}+n \right)}{n!}=1
\end{align}
Any member of the aforementioned family simply corresponds to a choice of the vectors $\vec{p}$ and $\vec{q}$ satisfying the above criteria.

>>>>

In furthering causal set theory it is crucial that we understand the kinematics of the theory. One avenue in this direction is the attempt to define a discrete counterpart of the gravitational action $S[\mathcal C]$ associated with a causal set $\mathcal C$, which furnishes the weight $e^{iS[\mathcal C]}$ in the graviational sum over histories. A proposal for the action of a causal set have recently been made \cite{Benincasa_Dowker:The_Scalar_Curvature_of_a_Causal_Set}, and for a number of special cases, it has been shown that for causal sets that are well-approximated by continuum spacetimes (in a sense that will be made clear below), the proposed action agrees with the Einstein-Hilbert action of the spacetime in the appropriate continuum limit.\mb{given what conditions?}

In the continuum, it is well known that the Einstein-Hilbert action, $S_{EH}$, is not the full story. In the presence of spacetime boundaries the gravitational action must include a boundary term $S_{GHY}$, the Gibbons-Hawking-York action, in order to yield a well-defined variational principle~\cite{Gibbons_Hawking_Boundary}. The contributions of this term play an essential role in particular in the quantum theory. For instance, in the calculation of the black hole entropy via the Euclidean path-integral, it is the boundary terms that produce the answer $A/4l_p^2$ necessary for the unification of black hole mechanics with thermodynamics. To give another example, in Regge calculus boundary terms are necessary in order that the quantum mechanical amplitudes satisfy the correct composition law and that they have the correct classical limit~\cite{hartlesorkin}.\mb{is this true?}

@@

In order to say we have a causal set analogue for a continuous expression we need a well defined procedure for relating the discrete theory to the continuum. This procedure is called a \textit{sprinkling}. A sprinkling is a Poisson process which provides a way to generate a causet from a $d$-dimensional Lorentzian manifold $ (M,g)$ by selecting certain points in $M$ to be the elements of $\mathcal{C}$, with an order relation given by the causal order of the manifold.\mb{certain points?} The number of points chosen in a region of spacetime volume, $V$, is a Poisson random variable. This means that the expected number of points in some region will be $\rho V$, where $\rho$ is the density of the sprinkling. The density is related to the discreteness scale, $l$, by $\rho=l^{-d}$ in $d$ spacetime dimensions. It is called a sprinkling as one can envisage the point selection process as a `sprinkling' of points into the manifold. If a causet, $\mathcal{C}$, can be generated with relatively high probability by a sprinkling into the manifold, $ (M,g)$, then we say that the manifold is a good approximation for the causal set, and that the causet can be \emph{faithfully embedded} in $M$.

@@

In order to give intuition to the ideas laid out in this paper it will be most convenient to consider spacetimes with boundary obtained by partitioning a manifold (without boundary) into two parts as follows. Let $(M,g)$ be a sufficiently well-behaved $d$-dimensional Lorentzian manifold. We assume that $(M,g)$ has finite volume and admits a \emph{spacelike partitioning} surface, $\Sigma$, defined as a spacelike closed compact surface in $M$, such that the causal past and future sets, $M^\pm=J^\pm (\Sigma)$ satisfy $M^+\cap M^-=\Sigma$. It then follows that $\partial M^\pm = \Sigma$, and further that no points in $M^+\setminus\Sigma$ precede any points in $M^-\setminus\Sigma$.~\!\footnote{If there did exist a $p\in M^+\setminus\Sigma$ and $q\in M^-\setminus\Sigma$ such that $p\preceq q$, then we would have $(q\in J^-(\Sigma) \text{ and } p\preceq q)\implies p\in J^-(\Sigma)\implies p\in M^-$, which would contradict $M^+\cap M^-=\Sigma$.} The Gibbons-Hawking-York boundary term for $M^\pm$ is then given by
\be\label{eq:GHYBT_in_continuum}
{S}^{(d)}_{GHY}\left[M^\pm\right]= \mp \frac{1}{l_p^{d-2}}\int_{\Sigma} K d\Sigma
\ee
where $l_p$ is the rationalised Planck length $l_p=(8\pi G)^{\frac{1}{d-2}}$ ($G$ denoting the gravitational constant in $d$ dimensions) and where $K$ is the trace of the extrinsic curvature $K_{\mu\nu}=h_{\mu}^\rho h_\nu^\sigma \nabla_\rho n_\sigma$ of $\Sigma$, defined here with future-pointing timelike unit normal covector $n_{\mu}=\partial_\mu S/\sqrt{g^{\mu\nu}\partial_\mu S\partial_\nu S}$. (We will work with a mostly plus convention for the metric, in which this translates into a past-pointing normal vector $n^{\mu}$).

Observe now that the integral in~\eqref{eq:GHYBT_in_continuum} can be thought of as the ``volume gradient'' across the surface $\Sigma$:
\be\label{eq:normal_deriv_boundary}
\int K d\Sigma = \frac{\partial}{\partial n}\int d\Sigma,
\ee
where the right hand side is the derivative of the area $\int d\Sigma$ as each point of $\Sigma$ is moved an equal distance along the unit normal vector, $n^{\mu}$ (corresponding to the rate of change of the surface volume \emph{backwards} in time, as $n^{\mu}$ is past-pointing).

This observation suggests a natural candidate for the discrete analogue of the boundary action associated with the surface $\Sigma$, for a causet that can be faithfully embedded in $M$. Spacetime volume in the causal set is obtained simply by counting the number of elements, and hence the volume gradient intuitively corresponds to the difference in the number of ``immediate neighbours'' to the future and to the past of a hypersurface. In order to make this notion precise, we need to define the discrete analogue of the hypersurface $\Sigma$, and also what it means for a causal set element to be an ``immediate neighbour'' to $\Sigma$.

Given a causet $\mathcal C$ that can be faithfully embedded in a manifold $M$ with a spacelike partitioning surface $\Sigma$, we obtain a natural partition of the causet into two parts $\mathcal{C}^+$ and $\mathcal{C}^-$, corresponding to the sets of elements that lie in $M^+=J^+(\Sigma)$ and $M^-=J^-(\Sigma)$. By virtue of $\Sigma$ being spacelike partitioning, the set $\mathcal C^-$ contains its own past, that is, any element in $\mathcal C$ that precedes at least one element in $\mathcal{C}^-$ is also in $\mathcal{C}^-$. A set with this property is known as a \emph{past stem}. Similarly, $\mathcal C^+$ is a \emph{future stem} given the analogous definition. We propose more generally that for any causet $\mathcal C$, a \emph{spacelike partition} is a non-trivial partition that splits $\mathcal{C}$ into two parts, $\mathcal{C}^-$ and $\mathcal{C}^+=\mathcal{C}\setminus\mathcal{C}^-$ \IGNORE{($\mathcal{C}=\mathcal{C}^-\cup\mathcal{C}^+$)}, such that $\mathcal{C}^-$ is a past stem (or, equivalently, that $\mathcal{C}^+$ is a future stem and $\mathcal{C}^- = \mathcal{C}\setminus\mathcal{C}^+$). A sprinkling into a manifold with a surface such as $\Sigma$ will of course produce a causal set with spacelike partition, but we shall refer to a partition of a causal set satisfying the above definition as spacelike even when the causet is not obtained via a sprinkling into some manifold.

We restrict our discussion to spacelike hypersurfaces, because the definition of the causet counterpart to the boundary action associated with a \emph{timelike} hypersurface is much less straight-forward, so much so that no satisfactory candidate has yet been found. The special case for null hypersurfaces deserves some comments. First, it appears that while the GHY boundary term is well defined for space-like and time-like boundaries in the continuum, it is an open question what the contribution from a null boundary is~\cite{Gibbons_Hawking_Boundary, Harris}.\mb{copied this from sumati's section before seeing her newest edits, so beware of repetition.} Second, in the discrete setting, the distinction between a null and a spacelike hypersurface loses its meaning to some extent, since any null hypersurface is ``infinitesimally close'' to a spacelike hypersurface. Hence a finite causet cannot distinguish a null hypersurface from a spacelike hypersurface. To see why this is, imagine a causal set obtained via sprinkling into a patch of $2$-dimensional Minkowski space. Figure~\ref{fig:low_density_sprinkling_with_null_and_spacelike} shows how, given a null surface that partitions the causet into two parts, we can tilt the surface ever so slightly to make it spacelike, while still preserving the partition. Figure~\ref{fig:high_density_sprinkling_with_null_and_spacelike} shows that even as we increase the density of the sprinkling we can tilt the surface by a smaller amount such that the partition remains unchanged. A finite causet faithfully embeddable into a manifold with a null hypersurface therefore has no way of knowing whether the hypersurface is null or spacelike. With these comments in mind, we return to the spacelike case but we shall return to the question of null boundaries below.

@@

\mb{rephrase}In the continuum, the GHY term is usually calculated for the future or past \emph{boundary} of a manifold, not for a partitioning hypersurface in it. If we wish to calculate the GHY term for future or past boundaries of causets, there are a couple issues we must deal with. First, if we can faithfully embed a causet $\mathcal{C}$ into a manifold $M$ with spacelike boundary, then the boundary of $M$ will induce a trivial partition of $\mathcal{C}$ (every element of $\mathcal{C}$ will lie in the bulk of $M$), thus the previous notion of the boundary term as a rate of change of spacetime atoms across a partition does not work. Second, it is necessary to to say a bounding surface of a causet if it is not faithfully embeddable in some manifold? Previously if the causet was not faithfully embeddable we could still define the causal set analogue of the surface as a partition of the causet, but now we have that either $\mathcal{C}^+$ or $\mathcal{C}^-$ will be the empty set. The first issue is not a problem, and we will see that a causal set GHY term can be found for a future (past) boundary of $M$ (the manifold that the causet has been faithfully embedded in) via some other expression in terms of the causet. This expression applies to any causet, and so must apply whether or not the causet is faithfully embeddable, but this runs us into the second issue above. What do we mean by a boundary of a causet? If one is given a causet with maximal and/or minimal elements, certain quantities can be calculated for that causet, like the GHY term we will propose in the next section. We will not provide any physical meaning to a \emph{future} or \emph{past boundary} of a causet, and shall merely state that they are abstract objects for which certain causal set quantities can be calculated. The reason we say that these quantities are being evaluated for the future (past) boundary of the causet is that given a causet that is faithfully embeddable in some manifold with future (past) boundary, the values of the quantities in question will agree with those of certain geometrical quantities for the continuum boundary, in some continuum limit of the causal set. We will henceforth mention future/past boundaries of causets only in the context of some quantity being evaluated for them.

@@

For a given causet $\mathcal C$, let us define the functions $\F{k}\left[\mathcal{C}\,\right]$, which count the number of elements in $\mathcal C$ that have exactly $k$ elements in their future, and the functions $\P{k}\left[\mathcal{C}\,\right]$, which count the number of elements which have exactly $k$ elements in their past. An ``$F_0$ element'' is then a \emph{maximal} element and a ``$P_0$ element'' is a \emph{minimal} element.

Given a causet, $\mathcal{C}$, with a spacelike partition so that $\mathcal C = \mathcal C^+ \cup\, \mathcal C^-$, we propose the following family of functions as the generalised causal set boundary action:
\be\label{general_boundary_sum}
S^{ (d)}_{GHY}\left[\mathcal{C}^-,\mathcal{C}^+;\vec{p}, \vec{q}\,\right]= \left (l/l_p\right)^{d-2} c_{d}
\left ( \sum_m p_m \F{m}\left[\mathcal{C}^- \right]
+  \sum_n q_n \P{n}\left[\mathcal{C}^+ \right]\right)
\ee
where the constant $c_{d}$ only depends on the spacetime dimension and is given by
\be\label{Cn}
c_{d}=\frac{d (d+1)}{ (d+2)}\left(\frac{V_{d-1}}{d}\right)^{\frac{2}{d}},
\ee
$V_d=\pi^{\frac{d}{2}}/\Gamma\left (\frac{d}{2}+1\right)$ denotes the volume of the unit $d$-ball and $\Gamma (t)$ is the gamma function. We have used $\vec{p}$ and $\vec{q}$ to stand for infinite dimensional vectors $ (p_0,...,p_m,..)$ and $ (q_0,...,q_n,..)$ respectively, where all the $p_m,\: q_n \in \mathbb{R}$. These vectors contain a finite number of non-zero entries corresponding to the coefficients of the $\F{m}$ and $\P{n}$ terms. We use the summation $\sum_m$ ($\sum_n$) to denote a sum that runs from $0$ to $m_{max}$ ($n_{max}$), where $m_{max}$ ($n_{max}$) is some integer, the value of which depends on the causet $\mathcal{C}^-$ ($\mathcal{C}^+$), for which all $\F{m}\left[\mathcal{C}^- \right]=0$ ($\P{n}\left[\mathcal{C}^+ \right]=0$) for any $m>m_{max}$ ($n>n_{max}$). Finite values for $m_{max}$ and $n_{max}$ will always exist for a finite causet. The vectors must be chosen such that they satisfy the following conditions.
\begin{align}\label{coefficient_relation1}
& \sum_m p_m \frac{\Gamma\left (\frac{1}{d}+m \right)}{m!}  + \sum_n q_n\frac{\Gamma\left (\frac{1}{d}+n \right)}{n!}=0
\\
& \label{coefficient_relation2}\sum_m p_m \frac{\Gamma\left (\frac{2}{d}+m \right)}{m!}  - \sum_n q_n\frac{\Gamma\left (\frac{2}{d}+n \right)}{n!}=1
\end{align}
Any member of the aforementioned family simply corresponds to a choice of the vectors $\vec{p}$ and $\vec{q}$ satisfying the above criteria.
